### 2022-09-30 AISTATS2023/paper.tex
updated real dataset part

\section{REAL-WORLD EXAMPLES}

In Real-World Datasets it is infeasible to obtain ground truth
information, therefore, we perform evaluation at two levels. First, we
compare visually NAME versus PDP with ICE plots. Second, we hold as
ground-truth the effects computed on the full training-set and we,
then, perform subsampling to evaluate the robustness of the
bin-splitting method.

\section{CONCLUSION}

>>>>

\section{REAL-WORLD EXAMPLE}

Here, we aim at demonstrating the usefuleness of uncertainty
quantification and the advantages of automatic bin-splitting, on the
real-world California Housing dataset~\citep{pace1997sparse}.

\paragraph{ML setup}

The California Housing is a largely-studied dataset with approximately
\(20000\) training instances, making it appropriate for robust
Monte-Carlo approximations. The dataset contains \(D=8\) features
describing building blocks of California, like latitude, longitude,
total number of people residing in the block etc., and the target is
the median house value inside the block. We exclude instances with
missing or outlier values, i.e. \(x_d^i > \hat{sigma}_j\) in any
feature and normalize them to have
\(\hat{\mu}_d = 0, \hat{\sigma_d}\). We split the dataset into
\(N_{tr} = 15639\) training and \(N_test = 3910\) test examples (80/20
split) and we fit a Neural Network with 3 hidden layers of 256, 128
and 36 units respectively. After 15 epochs using the Adam optimizer
with learning rate \(\eta = 0.02\), the model achieves a normalized
mean squared error (R-Squared) of \(0.25\) (0.75). In depth information
about preprocessing, training and evaluation are provided in the
Appendix.

\paragraph{Uncertainty Quantification}

In real-world datasets, it is infeasible to obtain the ground truth FE
for seamlessly evaluating the competitive methods. Therefore, the main
purpose of this part is to demonstrate the usefulness of uncertainty
quantification in NAME, i.e., illustrate that modeling the
heterogeneous effects is important for the interpretation of an ALE
plot. For this reason, Secondly, we discuss about the FE plots obtaing with NAME and
PDP-ICE.

\begin{figure}[h]
  \centering
  \includegraphics[width=.23\textwidth]{real_dataset_3/feature_1_ale_auto.pdf}
  \includegraphics[width=.23\textwidth]{real_dataset_3/feature_1_pdp_ice.pdf}\\
  \includegraphics[width=.23\textwidth]{real_dataset_3/feature_7_ale_auto.pdf}
  \includegraphics[width=.23\textwidth]{real_dataset_3/feature_7_pdp_ice.pdf}\\
  \caption{Figure 1}
  \label{fig:ex-synth-2-1}
\end{figure}

\paragraph{Bin Splitting}

For evaluating NAME in terms of bin-splitting we set-up the following
evaluation framework. We treat as ground-truth the effects computed on
the full training-set \(N=20000\) with dense fixed-size bin-splitting
(\(K=80\)). Given the big number of samples, we make the hypothesis
that the approximation with dense binning is close to the ground
truth. Afterwards we select less samples \(N=1000\) and we compare
NAME approximation with all possible fixed-size alternatives, in terms
of accuracy, i.e. we provide the quantities
\(\mathcal{L}^{\mu}, \mathcal{L}^{\sigma^2}, \mathcal{L}^{\rho^2}\).
\section{CONCLUSION}
